Fifa 2019 Dataset Linear Regression and Decision  Tree
```{r}

fifa19Data <- read.csv("D:\\Projects\\Machine Learning Datasets\\Dataset1.csv\\data.csv", 
                        header = T, na.strings = "", stringsAsFactors = F)
head(fifa19Data)

```
1.Starting with cleaning Dataset
1.0 Removing Unwanted Columns
```{r}
library(dplyr)
newdataFifa <- fifa19Data[,-c(1,2,3,5,6,7,10,11,20,21,23,24,25,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49,50,51,52,53,54)]
names(newdataFifa)
```
1.1 Removing symbols from rows.
```{r}
newdataFifa$Release.Clause <- gsub('[€]','',newdataFifa$Release.Clause)
# View(newdataFifa)
glimpse(newdataFifa)
newdataFifa$Value <- gsub('[€]','',fifa19Data$Value)
newdataFifa$Wage <- gsub('[€]','',fifa19Data$Wage)
# View(newdataFifa)
```
1.2 Converting M into millions and K into Thousands for Values, Wage and Release.clause (Read about the code)

```{r}
library(stringr)

newdataFifa <- newdataFifa %>% mutate(multiplier = ifelse(str_detect(Value, "K"), 1000, ifelse(str_detect(Value, "M"), 1000000, 1))) 

newdataFifa <- newdataFifa %>% mutate(Value = as.numeric(str_extract(Value, "[0-9]+")) * multiplier)
# View(newdataFifa)
newdataFifa <- newdataFifa %>% mutate(multiplier = ifelse(str_detect(Wage, "K"), 1000, ifelse(str_detect(Wage, "M"), 1000000, 1))) 

newdataFifa <- newdataFifa %>% mutate(Wage = as.numeric(str_extract(Wage, "[0-9]+")) * multiplier)
# View(newdataFifa)
newdataFifa <- newdataFifa %>% mutate(multiplier = ifelse(str_detect(Release.Clause, "K"), 1000, ifelse(str_detect(Release.Clause, "M"), 1000000, 1))) 

newdataFifa <- newdataFifa %>% mutate(Release.Clause = as.numeric(str_extract(Release.Clause, "[0-9]+")) * multiplier)
# View(newdataFifa)

```
1.3 Converting Preffered foot into 0,1 instead of left or right.
```{r}
str(newdataFifa)
newdataFifa$Preferred.Foot <- as.factor(newdataFifa$Preferred.Foot)
levels(newdataFifa$Preferred.Foot)[levels(newdataFifa$Preferred.Foot)== 'Left']<- '0'
levels(newdataFifa$Preferred.Foot)[levels(newdataFifa$Preferred.Foot)== 'Right']<- '1'
table(newdataFifa$Work.Rate)
```


```{r}
newdataFifa$Work.Rate <- as.factor(newdataFifa$Work.Rate)
levels(newdataFifa$Work.Rate)
# install.packages("rockchalk")
library(rockchalk)
newdataFifa$Work.Rate <- combineLevels(newdataFifa$Work.Rate, c("Low/ High","High/ High", "Medium/ High" ), newLabel = '2') 
newdataFifa$Work.Rate <- combineLevels(newdataFifa$Work.Rate, c("High/ Medium", "Medium/ Medium", "Low/ Medium" ), newLabel = '1') 
newdataFifa$Work.Rate <- combineLevels(newdataFifa$Work.Rate, c("Low/ Low","High/ Low", "Medium/ Low" ), newLabel = '0')
```

Adding all the columns related to skills of a player and remanimg to Skill and then taking an average of all.
```{r}
newdataFifa$Stats <- (newdataFifa$Crossing + newdataFifa$Finishing + newdataFifa$HeadingAccuracy + newdataFifa$ShortPassing +newdataFifa$Volleys + newdataFifa$Dribbling + newdataFifa$Curve + newdataFifa$FKAccuracy +newdataFifa$LongPassing + newdataFifa$BallControl + newdataFifa$Acceleration + newdataFifa$SprintSpeed +newdataFifa$Agility + newdataFifa$Reactions + newdataFifa$Balance + newdataFifa$ShotPower + newdataFifa$Jumping +newdataFifa$Stamina + newdataFifa$Strength + newdataFifa$LongShots + newdataFifa$Aggression + newdataFifa$Interceptions + newdataFifa$Positioning + newdataFifa$Vision + newdataFifa$Penalties + newdataFifa$Composure + newdataFifa$Marking )/ 27
glimpse(newdataFifa$Stats)
```

Removing Gk from the data set as they always have low release clause
```{r}

newdataFifa <- newdataFifa[which(newdataFifa$Position != 'GK'), ]
# View(newdataFifa$Position)
# View(newdataFifa)
#Removing the columns of various skills of players and the skills of GK as well
newDataFifa <- newdataFifa[,-c(16,17,18,19,20,21,22,23,24,25,26,27,28,29,30,31,32,33,34,35,36,37,38,39,40,41,42,43,44,45,46,47,48,49)]
# View(newDataFifa)
```
Converting Height into Centimeters
```{r}
library(gsubfn)
library(proto)
newDataFifa$Height <- as.numeric(gsubfn("(\\d)'(\\d+)", ~ as.numeric(x) * 30.48 + 
            as.numeric(y) * 2.54, sub('"', '', newDataFifa$Height)))
# View(newDataFifa)
```
Removing lbs from the value
```{r}
newDataFifa$Weight <- gsub('lbs','',newDataFifa$Weight)

# View(newDataFifa)
```
Converting Forward position like ST, LS, RS, LF, RF, LW, RW into Forward
Converting Forward position like CM, CAM, CDM, RDM, LDM, RCM,LCM, LM, RM into MidFielder
Converting Forward position like CB, RCB, LCB, LB, RB into Defender
```{r}
newDataFifa$Position <- as.factor(newDataFifa$Position)
levels(newDataFifa$Position)
newDataFifa$Position <- combineLevels(newDataFifa$Position, c("ST","LS", "RS", "LF", "RF", "LW", "RW" ,"CF"), newLabel = 'Forward')
newDataFifa$Position <- combineLevels(newDataFifa$Position, c("CM","CAM","LAM","CDM", "RAM","RDM", "LDM", "RCM", "LCM", "LM", "RM" ), newLabel = 'MidfFielder')
newDataFifa$Position <- combineLevels(newDataFifa$Position, c("CB","RCB", "LCB","LWB","RWB","LB", "RB" ), newLabel = 'Defender') 
# View(newDataFifa)
```
Converting Special into 0 as we don't need that and neither it has any affect on the result.
```{r}
newDataFifa$Special <- -c(newDataFifa$Special)
# View(newDataFifa)
```
Removing the NA from the Data
```{r}
newDataFifa <- na.omit(newDataFifa)
# View(newDataFifa)
```
Converting the Contract valid untill to single year
```{r}
newDataFifa$Contract.Valid.Until <- as.numeric((newDataFifa$Contract.Valid.Until))
# View(newDataFifa)
```
Final cleaned Data set with columns which were not required removed.
```{r}
FinalFifa19 <- newDataFifa[, -c(6,17)]
class(FinalFifa19$Weight)
FinalFifa19$Weight <- as.numeric(FinalFifa19$Weight) 
class(FinalFifa19$Weight)
```
```{r}
install.packages("caret")
library(caret)
# set.seed(14)
# ind = createDataPartition(FinalFifa19$Release.Clause, times = 1, p = 0.8, list = F) 
# Fifadata_train = FinalFifa19[ind, ] 
# Fifadata_test = FinalFifa19[-ind, ]
# View(FinalFifa19)

set.seed(123)
s1 <- sample(1:nrow(FinalFifa19), 0.7*nrow(FinalFifa19))
Fifadata_train <- FinalFifa19[s1,]
Fifadata_test <- FinalFifa19[-s1,]

str(FinalFifa19)

library(dplyr)
reg <- lm(Release.Clause ~ ., data = Fifadata_train)
summary(reg)
```


```{r}
#removed insignificant variables one by one based on significancev- Backward Selection
reg <- lm(Release.Clause ~ . -Work.Rate -Skill.Moves -Stats -Preferred.Foot -Weak.Foot -Weight -Height, data = Fifadata_train)
summary(reg)


```
```{r}


#pred1 <- reg %>% predict(Fifa_test)
#plot(pred1,Fifa_test$Release.Clause,xlab="predicted",ylab="actual")

```
```{r}
# predicting Release Clause on train dataset
predTrain <- predict(reg, newdata = Fifadata_train)
#summary(predTrain)
library(dplyr)
# calculating RMSE for training dataset
trainRMSE <- mean((Fifadata_train$Release.Clause - predTrain)**2) %>%sqrt()

trainRMSE
```
Normalization of RLC and wages and values.

```{r}
# install.packages("Metrics")
library(Metrics)

# calculating MAE for training dataset
trainMAE <- mae(Fifadata_train$Release.Clause, predTrain)
trainMAE
```


```{r}
# predicting prices on test dataset
predTest <- predict(reg, newdata = Fifadata_test)
library(dplyr)
# calculating RMSE for test dataset
testRMSE <- mean((Fifadata_test$Release.Clause - predTest)**2) %>%
  sqrt()
testRMSE
```


```{r}
# calculating MAE for test dataset
testMAE <- mae(Fifadata_test$Release.Clause, predTest)
testMAE
```

```{r}
library(rpart)

names(Fifadata_train)
regDT <- rpart(Release.Clause ~ ., data = Fifadata_train)
regDT
```

```{r}
predTrainDT <- predict(regDT, newdata = Fifadata_train)
predTrainDT
```


```{r}
cor(predTrainDT, Fifadata_train$Release.Clause)
```
 
```{r}
MAE <- function(actual, predicted) {
  mean(abs(actual - predicted))
}

MAEDT_Train <- MAE(predTrainDT, Fifadata_train$Release.Clause)
MAEDT_Train
```
```{r}
RMSEDT_Train <- mean((Fifadata_train$Release.Clause - predTrainDT)**2) %>%
  sqrt()
RMSEDT_Train
```
# predicting on test data
```{r}
predTestDT <- predict(regDT, newdata = Fifadata_test)

cor(predTestDT, Fifadata_test$Release.Clause)
```
```{r}
MAEDT_Test <- MAE(predTestDT, Fifadata_test$Release.Clause)
MAEDT_Test
```
```{r}
RMSEDT_Test <- mean((Fifadata_test$Release.Clause - predTestDT)**2) %>%
  sqrt()
RMSEDT_Test
```

